Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-06-08 paper_jasa.tex
added subsection which follows up checking lowest p-value pick
minimum p-value assumption holds

>>>>

\subsection{Do people tend to pick the lowest $p$-value?}

This section takes the data and looks at the assumption made for the early expected power.

\begin{figure*}[hbtp]
   \centering
       \scalebox{0.6}{\includegraphics{p_val_rank_counts.pdf}}
       \caption{Rank of p-values in a lineup of size 20 and the number of subjects choosing that plot in the lineup of experiment 1 with raw data (nothing is dropped). This indicates that most of the subjects pick the plot with minimum p-value (rank 1). There are subjects choosing the lineups with highest p-value(rank 20) but we can attribute this behavior to the type-I error. Can we?}
       \label{fig:P-val_rank}
\end{figure*}
